Happiness versus Income Awareness

### 2022-02-28 outputs/paper/Paper2-copy.Rmd
step2

@@

```{r include=FALSE}
library(haven)
library(tidyverse)
```

```{r include=FALSE}
survey_data = read_dta("Raw-Norwegian-Monitor-Survey-Data.dta", encoding = 'latin1')
country_data = read_dta("google_searches_by_country.dta", encoding = 'latin1')
time_data = read_dta("google_searches_over_time.dta", encoding = 'latin1')
names_data = read_dta("names_browsing_skattelister.dta", encoding = 'latin1')
```

@@

## Limitations
There existed very limited used of the online tax lists for the purpose of learning salary. The actual percentage turned out to be only 26 percent of the individuals and may be only for the purpose of snooping not researching. Plus, the nature of the data was described as "completely useless" for salary comparisons practices(NRK 2008). On top of that, the Norwegian tax records reveal comprehensive income including gains outside of the payroll which puts additional uncertainties comparing to the benchmark of the website of state employees studied in Card et al. (2012).

@@

# References

>>>>

The analysis will be conducted in R (@citeR), and the package we will use is tidyverse[@citetidyverse]. All graphs will be created using function ggplot2[@citeggplot2]. The packages knitr [@knitr] are also used to generate the R markdown report.

@@

```{r include=FALSE}
library(tidyverse)
library(haven)
library(tidyr)
library(reshape2)
```

```{r include=FALSE}
survey_data = read_dta("Raw-Norwegian-Monitor-Survey-Data.dta", encoding = 'latin1')
country_data = read_dta("google_searches_by_country.dta", encoding = 'latin1')
time_data = read_dta("google_searches_over_time.dta", encoding = 'latin1')
#names_data = read_dta("names_browsing_skattelister.dta", encoding = 'latin1')
```

@@

## Limitations
There existed very limited used of the online tax lists for the purpose of learning salary. The actual percentage turned out to be only 26 percent of the individuals and may be only for the purpose of snooping not researching. Plus, the nature of the data was described as "completely useless" for salary comparisons practices[@citenrk]. On top of that, the Norwegian tax records reveal comprehensive income including gains outside of the payroll which puts additional uncertainties comparing to the benchmark of the website of state employees studied in [@citecard].

@@

# Reference
